---
title: "Voronoi Diagrams with ggvoronoi"
author: "Robert Garrett"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Voronoi Diagrams with ggvoronoi}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(ggvoronoi)
library(tidyverse)
```


With ggvoronoi we can easily draw Voronoi diagram heatmaps. 
A Voronoi diagram draws the nearest neighbor regions around a set of points, and by specifying a fill argument we can turn that into a heatmap!
Applications of voronoi diagrams include:

- finding the one nearest neighbor to a given point
- interpolating a set of points without using a raster
- creating useful and appealing graphics

## Example 1: Voronoi Diagram Simulation

Let's inspect the points dataset inluded in ggvoronoi.

```{r 1a}
library(ggvoronoi)
library(tidyverse)

ggplot(points)+
  geom_point(aes(x,y,color=fill))
```

All this data has is a set of x and y coordinates, along with "fill", a distance calculation that we will use to color the voronoi diagram.

ggvoronoi can use this set of points to quickly plot a Voronoi diagram, working with the ggplot2 framework:

```{r 1b}
ggplot(points)+
  geom_voronoi(aes(x,y,fill=fill))
```

Additionally, we can use the stat_voronoi function directly to specify which ggplot 2 geom we would like to use.
This is most useful when we are interested in plotting only the borders of the diagram:

```{r 1c}
ggplot(points,aes(x,y))+
  stat_voronoi(geom="path")+
  geom_point()
```

